Bioconductor workflow for single-cell RNA sequencing: Dimensionality reduction, clustering, and lineage inference

### 2017-06-27 workflow/workflow.Rmd
Edits to text.

The `zinbDimRed` function can also be used to perform dimensionality reduction, where the user-supplied dimension `K` of the low-dimensional space is set here to `K = 50`. The resulting low-dimensional matrix `W` can be visualized in two dimensions by performing multi-dimensional scaling (MDS) using the Euclidian distance. To verify that `W` indeed captured the biological signal of interest, we plotted the MDS of `W` with colors corresponding to the original published clusters (Figure \@ref(fig:mdsW)).

>>>>

The `zinbDimRed` function can also be used to perform dimensionality reduction, where in this workflow the user-supplied dimension `K` of the low-dimensional space is set to `K = 50`. The resulting low-dimensional matrix `W` can be visualized in two dimensions by performing multi-dimensional scaling (MDS) using the Euclidian distance. To verify that `W` indeed captures the biological signal of interest, we display the MDS results with colors corresponding to the original published clusters (Figure \@ref(fig:mdsW)).
